\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
More AV comments flagged in red, #209

We found that the distributions for the \StageTwo agents to be qualitatively
very similar to those for the \StageOne agents. The differences are: 1) the
maximum effort possible at \StageTwo is smaller, simply because fewer subjects
were available to be classified, and 2) the information generated per agent was
slightly higher at \StageTwo, just because the subjects had (on average) higher
probability
MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER??.

@@

However, identification failures (DEFINE WHAT YOU MEAN BY IDENTIFICATION FAILURES around 60\%, from inspection of a random sample)
seem to be due to the statistical noise associated with
the many short, semi-random direction kicks arising from classifications made by
low skill, inexperienced
classifiers (\Sref{sec:results:crowd}). ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in when needed. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to acquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.

>>>>

We found that the distributions for the \StageTwo agents to be qualitatively
very similar to those for the \StageOne agents. The differences are: 1) the
maximum effort possible at \StageTwo is smaller, simply because fewer subjects
were available to be classified, and 2) the information generated per agent was
slightly higher at \StageTwo, just because the subjects had (on average) higher
probability.

\flag{AV}{MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER?}

@@

However, identification failures \flag{AV}{DEFINE WHAT YOU MEAN BY IDENTIFICATION
FAILURES} around 60\%, from inspection of a random sample) seem to be due to the
statistical noise associated with the many short, semi-random direction kicks
arising from classifications made by low skill, inexperienced classifiers
(\Sref{sec:results:crowd}). \flag{AV}{ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE
RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.} While improved training will
help reduce this effect, it is here that targeted task assignment could also
help improve system performance, by bringing higher skill volunteers in when
needed. We advertised \StageTwo of the current project to all registered users;
it was taken up by \StageOne veterans with a broad range of skill, and also
picked up a significant number of new users who did not have enough time to
acquire high skill (since \StageTwo was quite short): of the 1964 volunteers who
took part in the \StageTwo classification round, only 774 were veterans from
\StageOne.
